\bf A Concise Survey on Statistical Analysis in Bike Lane Research

### 2023-11-13 Manuscript/Manuscript.tex
added conclusion

>>>>

In conclusion, this survey of statistical research on bike lanes offers a current snapshot of frequently used methods in the analysis of bike lanes. The significance of bike lanes in increasing cycling highlights the need for continued research and innovative statistical analysis to understand how to overcome the challenges of congestion, safety, and sustainability in transportation. This supports the efforts of enhancing cycling infrastructure for the benefits of individuals experiences while cycling and the betterment of entire communities.
